Publications

### 2025-08-19 papers.qmd
TG2 publications and further suggested publications are now separate and their own title (#)

---
title: "TG2 Publications"
---

@@

# Suggested Publications

>>>>

---
title: "Publications"
---

# Topic Group 2 (TG2) Publications

These publications were written as part of STRATOS-TG2. Their aim is guidance on the topic of variable and functional form selection.

@@

# Further Suggested Publications

Here we list a number of textbooks and papers that were written outside of STRATOS-TG2 by TG2 members or other authors. These materials are endorsed here because they fit the aim of guidance on selection of variables and functional forms in multivariable modeling.
